\documentclass[11pt]{article}
\usepackage{notes}
\usepackage{faktor}

\newcommand{\thiscoursecode}{PMATH 348}
\newcommand{\thiscoursename}{Fields and Galois Theory}
\newcommand{\thisprof}{Yu-Ru Liu}
\newcommand{\me}{Kevin Cheng}
\newcommand{\thisterm}{Winter 2018}

\newcommand{\cyclic}[1]{\left\langle #1 \right\rangle}
\newcommand{\quotient}[2]{\faktor{#1}{#2}}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}
\DeclareMathOperator{\Frac}{Frac}
\DeclareMathOperator{\ch}{ch}
\DeclareMathOperator{\Sub}{Sub}

\hypersetup
{pdfauthor={\me},
pdftitle={\thiscoursecode \thisterm Lecutre Notes},
pdfsubject={\thiscoursename}
pdflang={English}}

\begin{document}

\begin{titlepage}
\begin{centering}
{\scshape\LARGE University of Waterloo \par}
\globe
{\huge\bf \thiscoursecode}\\
{\scshape\Large \thiscoursename}\\
\vspace{.3cm}
{\scshape Prof. \thisprof~\textbullet~\thisterm\par}
\end{centering}
\sectionline
\tableofcontents
\sectionline
\thispagestyle{empty}
\end{titlepage}

\section{Introduction}
\subsection{Polynomial Equations}
Consider the quadratic equation. Let $ax^2 + bx + c = 0$ with the leading
coefficient $a \neq 0$, then we have that,
\begin{equation*}
x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
\end{equation*}
We notice immediately that there are a couple of operations that are involved in
this equation.
\begin{definition}
An expression involving only addition, subtraction, multiplication, division and
radicals is called a \underline{radical}. These operations are denoted by $+, -,
\times, \div$ and $\sqrt[n]{\cdot}$
\end{definition}
The natural question that is raised is the extension to higher dimensions.
\subsection{Cubic Equations}
All cubic equations can be reduced to the following equation,
\begin{align*}
x^3 + px = q
\end{align*}
for some $p, q \in \C$. A solution to the above equation is of the form
\begin{equation*}
x = \sqrt[3]{\frac{q}{2} + \sqrt{\frac{p^3}{27} + \frac{q^2}{4}}} +
\sqrt[3]{\frac{q}{2} - \sqrt{\frac{p^3}{27} + \frac{q^2}{4}}}\tag{Cardano's
Formula}
\end{equation*}
\subsection{Quartic Equations}
A radical solution can be obtained by reducing a quartic to a cubic equation.
\subsection{Quintic Equations}
\begin{itemize}
\item General radical solutions were attempted by Euler, B\'ezout and Lagrange
without success
\item In 1799, Ruffini gave a 516 page proof about the insolvability of quintic
equations. His Proof was ``almost right''
\item In 1824, Abel filled the gap in Ruffini's proof.
\end{itemize}
We can now ask ourselves, given a quintic equation, is it solvable by radicals?
This question seems to be too hard, so we ask, suppose that a radical solution
exists. How does its associated quintic equation look like?\\

\underline{Two main steps in Galois Theory}
\begin{enumerate}
\item Link a root of a quintic equation, say $\alpha$ to $\Q(\alpha)$, the
smallest field containing $\Q$ and $\alpha$. $\Q(\alpha)$ is a field. So it has
more structures to be played with than $\alpha$; however, our knowledge of
$\Q(\alpha)$ is still too little to answer the question. For example, we do not
know how many intermediate fields, $E$ between $\Q$ and $\Q(\alpha)$.
What we mean is how many fields $E$ satisfy
\begin{equation*}
\Q \subseteq E \subseteq \Q(\alpha).
\end{equation*}
\item Link the field $\Q(\alpha)$ to a group. More precisely, we associate
$\Q(\alpha)/\Q$ to the group
\begin{equation*}
\Aut_\Q (\Q(\alpha)) = \bigg\{\Psi : \Q(\alpha) \to \Q(\alpha)\>\text{an
isomorphism and } \Psi|_\Q = 1_\Q\bigg\}
\end{equation*}
It can be shown that if $\alpha$ is ``good'', say algebraic, $\Aut_\Q
(\Q(\alpha))$ is finite. If $\alpha$ is ``very good'', say constructable, the
order of $\Aut_\Q (\Q(\alpha))$ is in certain forms. Moreover, there is a
one-to-one correspondence between the intermediate fields between $\Q(\alpha)$
and $\Q$ and the subgroups of $\Aut_\Q (\Q(\alpha))$.
\end{enumerate}

It follows that given some ``good'' $\alpha$, we have that the
intermediate fields of $\Q(\alpha)$ and $\Q$ are indeed finitely many. This
introduces \underline{Galois Theory}; the interplay between fields and groups.

\pagebreak
\section{Field Extensions}
\subsection{Degree of Extensions}
\begin{definition}
If $E$ is a field containing another field $F$, we say $E$ is a
\underline{field extension} of $F$, denoted by $\quotient EF$.
\end{definition}
If $\quotient{E}{F}$ if a field extension, we can view $E$ as a vector space
over $F$.
\begin{enumerate}
\item \underline{Addition}: For $e_1, e_2 \in E$, $e_1 + e_2 \coloneqq e_1 +
e_2$ (addition in $E$)
\item \underline{Scalar Multiplication}: For $c \in F, e \in E$, $c \cdot e
\coloneqq ce$ (multiplication in $E$)
\end{enumerate}
\begin{definition}
The dimension of $E$ over $F$ (viewed as a vector space) called the
\underline{degree} of $E$ over $F$, denoted by $[E:F]$. If $[E:F] < \infty$, we
say $\quotient EF$ is a \underline{finite extension}. Otherwise,
$\quotient{E}{F}$ is an \underline{infinite extension}.
\end{definition}
\begin{example}
$[\C : \R] = 2$ is a  finite extension since $\C \cong \R + \R i$, with $i^2 =
-1$.
\end{example}
\begin{example}
Let $F$ be a field. Then $[F(x) : F]$ is $\infty$ since $\{1, x, x^2, \dots\}$
are linearly independent over $F$.
\end{example}
\begin{remark}
$F[x] = \{f(x) = a_0 + a_1x + \dots + a_nx^n : a_i \in F, n \in \N \cup
\{0\}\}$, the polynomial ring of $F$.
\end{remark}
\begin{remark}
$F(x) = \{\frac{f(x)}{g(x)} : f(x), g(x) \in F[x]\}$, the fraction
field of the polynomial ring of $F$. 
\end{remark}
\begin{theorem} \label{theorem1}
If $E/K$ and $K/F$ are finite field extensions, then $\quotient{E}{F}$ is a
finite field extension and
\begin{equation*}
[E:F] = [E:K][K:F]
\end{equation*}
In particular, $K$ is an intermediate field of an field extension
$\quotient{E}{F}$, then $[K:F]\>\big|\> [E:F]$. 
\end{theorem}
\begin{proof}
Suppose $[E:K]=m$ and $[K:F] = n$. Let $\{a_i,\dots,a_m\}$ be a basis of
$E/K$ and $\{b_1, \dots, b_n\}$ be a basis of $K/F$. It suffices to show
$\{a_ib_j:1 \leq i \leq m, 1 \leq j \leq n\}$ is a basis of $\quotient{E}{F}$.\\

\begin{claim}
Every element of $E$ is a linear combination of $\{a_ib_j\}$ over $F$.
\end{claim}

For $e \in E$, we have
\begin{equation*}
e = \sum^m_{i=1} k_ia_i 
\end{equation*}
with $k_i \in K$. Also, for each $k_i \in K$, we have
\begin{equation*}
k_i = \sum^n_{j=1} c_{ij}b_j 
\end{equation*}
with $c_{ij} \in F$. Thus,
\begin{equation*}
e = \sum^m_{i=1} \sum^n_{j=1} c_{ij}b_ja_i.
\end{equation*}

\begin{claim}
The set $\{a_ib_j:1\leq i\leq m,1\leq j\leq n\}$ is linearly independent
over $F$.
\end{claim}
Suppose that $$\sum_{i=1}^m\sum_{j=1}^nc_{ij}b_ja_i=0$$ with $c_{ij}\in F$.
Since $\sum_{j=1}^nc_{ij}b_j\in K$ and $\{a_1,\dots,a_m\}$ are independent over
$K$. We have $$\sum_{j=1}^nc_{ij}b_j=0.$$ Since $\{b_1,\dots,b_n\}$ are
independent over $F$, we have $c_{ij}=0$.\\

Combining both claims, we see that $\{a_ib_j,1\leq i\leq m,1\leq j\leq n\}$ is a
basis of $\quotient{E}{F}$ and we have $[E:F]=[E:K][K:F]$.
\end{proof}

\subsection{Algebraic and Transcendental Extensions}
\begin{definition}
Let $\quotient{E}{F}$ be a field extension and $\alpha \in E$. We say $\alpha$
is \underline{algebraic over $F$} if there exists $f(x) \in F[x]\setminus \{0\}$
with $f(\alpha) = 0$. Otherwise, $\alpha$ is \underline{transcendental over
$F$}.
\end{definition}
\begin{example}
$\frac{c}{d} \in \Q$, $\sqrt 2$ $\sqrt[3]{7} + 2i$ are algebraic over $\Q$
(see Assignment 1) but $e$ (Hermite, 1873) and $\pi$ (Lindemann, 1882) are
transcendental over $\Q$.
\end{example}
Let $\quotient{E}{F}$ be a field extension and $\alpha \in E$. Let $F[\alpha]$
denote the smallest subfield of $E$ containing $F$ and $\alpha$. For $\alpha,
\beta \in E$, we define $F[\alpha, \beta]$ and $F(\alpha, \beta)$ similarly.
\begin{definition}
If $F = F(\alpha)$ for some $\alpha \in E$, we say $E$ is a \underline{simple
extension} of $F$.
\end{definition}
\begin{definition}
Let $R_1$ and $R_2$ be two rings which contain a field $F$. A ring homomorphism
$\Psi: R_1 \to R_2$ is said to be a \underline{$F$-homomorphism} if $\Psi|_F =
1_F$.
\end{definition}
\begin{theorem} \label{theorem2}
Let $\quotient{E}{F}$ be a field extension and $\alpha \in E$. If $\alpha$ is
transcendental over $F$, then
\begin{equation*}
F[\alpha] \cong F[x] \quad \text{and} \quad F(\alpha) \cong F(x)
\end{equation*}
In particular, $F[\alpha] \neq F(\alpha)$.
\end{theorem}
\begin{remark}
In fact, if $\alpha$ is algebraic, indeed $F[\alpha] = F(\alpha)$.
\end{remark}
\begin{proof}
Let $\Psi:F(x) \to F(\alpha)$ be the unique $F$-homomorphism defined by $\Psi(x)
= \alpha$. Thus, for $f(x), g(x) \in F[x], g(x) \neq 0$, 
$$\Psi\bigg(\frac{f(x)}{g(x)}\bigg) = \frac{f(\alpha)}{g(\alpha)} \in
F(\alpha).$$ 
Notice that this is indeed a well-defined map as $g(x) \neq 0$ implies
$g(\alpha) \neq 0$ since $\alpha$ is transcendental. Since $F(x)$ is a field and
$\ker(\Psi)$ is an ideal of $F(x)$, we have $\ker(\Psi) = F(x)$ or trivial. Thus
$\Psi = 0$ or $\Psi$ is injective. Since $\Psi(x) = \alpha \neq 0$, $\Psi$ must
be injective. Also, since $F(x)$ is a field, $\im(\Psi)$ contains a field
generated by $F$ and $\alpha$, in other words, $F(\alpha) \subseteq \im(\Psi)$.
Thus, $\im(\Psi) = F(\alpha)$ and $\Psi$ is surjective. It follows that
$\Psi$ is an isomorphism and we have
\begin{equation*}
F[\alpha] \cong F[x] \quad \text{and} \quad F(\alpha) \cong F(x).
\end{equation*}
\end{proof}
\begin{theorem} \label{theorem3}
Let $\quotient{E}{F}$ be a field extension and $\alpha \in E$. If $\alpha$ is
algebraic over $F$, there exists a unique monic irreducible polynomial $p(x) \in
F[x]$ such that there exists a $F$-homomorphism
\begin{equation*}
\Psi:\quotient{F[x]}{\cyclic{p(x)}} \to F[\alpha] \quad \text{with } \Psi(x) =
\alpha
\end{equation*}
from which we conclude $F[\alpha] \cong F(\alpha)$.
\end{theorem}
\begin{proof}
Consider the unique $F$-homomorphism $\Psi: F[x] \to F[\alpha]$ defined by
$\Psi(x) = \alpha$. Thus, for $f(x) \in F[x]$, we have $\Psi(f) = f(\alpha)$.
Since $F[x]$ is a ring, $\im(\Psi)$ contains a ring generated by $F$ and
$\alpha$, in other words, $F[\alpha] \subseteq \im(\Psi)$. Thus, $\im(\Psi) =
F[\alpha]$.\\
Let
\begin{equation*}
I = \ker(\Psi) = \{f(x) \in F[x] : f(\alpha) = 0 \}.
\end{equation*}
Since $\alpha$ is algebraic, $I \neq \{0\}$. We have $\quotient{F[x]}{I} \cong
\im(\Psi) = F[\alpha] \subseteq F(\alpha)$, a subring of a field $F(\alpha)$.
Thus, $\quotient{F[x]}{I}$ is an integral domain so $I$ is a prime ideal. It
follows that $I = \cyclic{p(x)}$, where $p(x)$ is irreducible. If we assume
$p(x)$ is monic, then it is unique. It follows that
\begin{equation*}
\quotient{F[x]}{\cyclic{p(x)}}\cong F[\alpha].
\end{equation*}
Since $p(x)$ is irreducible, $\quotient{F[x]}{\cyclic{p(x)}}$ is a field. So
$F[\alpha]$ is a field. It follows that $F[\alpha] = F(\alpha)$.
\end{proof}
\begin{definition}
If $\alpha$ is algebraic over a field $F$, the unique monic polynomial
irreducible polynomial $p(x)$ in \cref{theorem3} is called the
\underline{minimal polynomial of $\alpha$ over $F$}.
\end{definition}
\begin{remark}
From the proof of \cref{theorem3}, if $f(x) \in F[x]$ with $f(\alpha) = 0$, then
$p(x) \big| f(x)$.
\end{remark}
\begin{theorem} \label{theorem4}
Let $\quotient{E}{F}$ be a field extension and $\alpha \in E$.
\begin{enumerate}
\item $\alpha$ is transcendental over $F$ if and only if $[F(\alpha):F]$ is
$\infty$.
\item $\alpha$ is algebraic over $F$ if and only if $[F(\alpha):F] < \infty$.
\end{enumerate}
Moreover, if $p(x)$ is the minimal polynomial of $\alpha$ over $F$, we have
$[F[\alpha]:F] = \deg(p)$ and $\{1, \alpha, \alpha^2, \dots,
\alpha^{\deg (p) - 1}\}$ is a basis of $\quotient{F(\alpha)}{F}$.
\end{theorem}
\begin{proof}
It suffices to prove the forward direction for each statement as the inverse
direction implies the other statement.
\begin{enumerate}
\item {\bf Forwards}: From \cref{theorem2}, if $\alpha$ is transcendental over
$F$, then $F(x) \cong F(\alpha)$. In $F(x)$, the elements $\{1, x, x^2, \dots\}$
are linearly independent over $F$. Thus, $[F(\alpha):F]$ is $\infty$.\\
\item {\bf Forwards}: From \cref{theorem3}, if $\alpha$ is algebraic over $F$,
$\quotient{F[x]}{\cyclic{p(x)}} \cong F(x)$ with the map $x \mapsto \alpha$.
Note that,
\begin{equation*}
\quotient{F[x]}{\cyclic{p(x)}} \cong \{r(x) \in F[x]: \deg(r) < \deg(p)\}
\tag{$\deg(0) = -\infty$}
\end{equation*}
Thus, $\{1, x, x^2, \dots, x^{\deg(p) - 1}\}$ forms a basis for
$\quotient{F[x]}{\cyclic{p(x)}}$. It follows that $[F(\alpha): F] =
\deg(p)$ and $\{1, \alpha, \alpha^2, \dots,
\alpha^{\deg (p) - 1}\}$ is a basis of $\quotient{F(\alpha)}{F}$.
\end{enumerate}
\end{proof}
\begin{theorem}\label{theorem5}
Let $\quotient{E}{F}$ be a field extension. If $[E:F] < \infty$, then there
exists $\alpha_1, \dots, \alpha_n \in E$ such that
\begin{equation*}
F \subsetneq F(\alpha_1) \subsetneq \dots \subsetneq F(\alpha_1, \dots,
\alpha_n) = E.
\end{equation*}
\end{theorem}
\begin{proof}
We proceed with induction on $[E:F]$. If $[E:F] = 1$, $E=F$. Suppose that $[E:F]
> 1$ and the statement holds for any field extension $\quotient{\tilde
E}{\tilde F}$ with $[\tilde E : \tilde F] < [E:F]$. Let $\alpha_1 \in
\quotient{E}{F}$. By \cref{theorem1},
\begin{equation*}
[E:F] = [E:F(\alpha_1)][F(\alpha_1) : F].
\end{equation*}
Since $[F(\alpha):F] > 1$, we have $[E:F] > [E:F(\alpha_1)]$. By induction
hypothesis, there exists $\alpha_2, \dots, \alpha_n$ such that
\begin{equation*}
F(\alpha_1) \subsetneq \dots \subsetneq F(\alpha_1, \dots, \alpha_n) = E.
\end{equation*}
Thus, we have
\begin{equation*}
F \subsetneq F(\alpha_1) \subsetneq \dots \subsetneq F(\alpha_1, \dots,
\alpha_n) = E.
\end{equation*}
as desired.
\end{proof}
\begin{definition}
A field extension $\quotient{E}{F}$ is \underline{algebraic} if every $\alpha
\in E$ is algebraic over $F$. Otherwise, it is \underline{transcendental}.
\end{definition}
\begin{theorem} \label{theorem6}
Let $\quotient{E}{F}$ be a field extension. If $[E:F] < \infty$, then
$\quotient{E}{F}$ is algebraic.
\end{theorem}
\begin{proof}
Suppose $[E:F] = n$. For $\alpha \in E$, the elements $\{1, \alpha, \dots,
\alpha^n\}$ are not linearly independent over $F$. Thus, there exists $c_i \in
F$ for all $i = 0, \dots , n$, not all 0, such that
\begin{equation*}
\sum^n_{i = 0} c_i\alpha^i = 0
\end{equation*}
Thus, $\alpha$ is a root of the polynomial $\sum^n_{i = 0} c_i\alpha^i \in
F[x]$ so it is algebraic over $F$.
\end{proof}
\begin{theorem}
Let $\quotient{E}{F}$ be a field extension. Define,
\begin{equation*}
L \coloneqq \{\alpha \in E: [F(\alpha) : F] < \infty\}.
\end{equation*}
Then $L$ is an intermediate field of $\quotient{E}{F}$.
\end{theorem}
\begin{proof}
If $\alpha, \beta \in L$ with $\beta \neq 0$, we need to show that $\alpha \pm
\beta, \alpha\beta, \frac{\alpha}{\beta} \in L$. By definition of $L$, we have
$[F(\alpha)] < \infty$ and $[F(\beta) : F] < \infty$. Consider the field
$F(\alpha, \beta)$. Since the minimal polynomial of $\alpha$ over $F(\beta)$
divides the minimal polynomial of $\alpha $ over $F$ (the minimal polynomial
$\alpha$ over $F$, say $p(x) \in F[x]$, is also a polynomial over $F(\beta)$.
In otherwords, $p(x) \in F(\beta)[x]$ such that $p(\alpha) = 0$), we have
\begin{equation*}
[F(\alpha, \beta):F(\beta)] \leq [F(\alpha):F].
\end{equation*}
Combining this with \cref{theorem1}, we have
\begin{align*}
[F(\alpha,\beta):F] &= [F(\alpha,\beta):F(\beta)][F(\beta):F]\\
&\leq [F(\alpha):F][F(\beta):F]
\end{align*}
Since $\alpha + \beta \in F(\alpha, \beta)$, it follows that
\begin{equation*}
[F(\alpha + \beta):F] \leq [F(\alpha, \beta):F] < \infty,
\end{equation*}
so $a+b\in L$. We can follow a similar line to show $\alpha - \beta,
\alpha\beta, \frac{\alpha}{\beta} \in L$. So $L$ is a field.
\end{proof}
\begin{definition}
Let $\quotient{E}{F}$ be a field extension. The set,
\begin{equation*}
L \coloneqq \{\alpha \in E: [F(\alpha) : F] < \infty\}
\end{equation*}
is called the \underline{algebraic closure of $F$ in $E$}.
\end{definition}
\begin{definition}
A field $F$ is \underline{algebraically closed} if for any algebraic extension
$\quotient{E}{F}$, we have $E = F$.
\end{definition}
\begin{example}
By the Fundamental Theorem of Algebra, $\C$ is algebraically closed.
\end{example}

\subsection{Eisenstein's Criterion}
\begin{definition}
Let $f(x) = a_nx^n + \dots + a_1x + a_0 \in \Z[x]$. We say $f(x)$ is
\underline{primitive} if $a_n > 0$ and $\gcd(a_0, \dots, a_n) = 1$. 
\end{definition}
\begin{lemma*}
Every non-zero polynomial $f(x) \in \Q[x]$ can be written uniquely as a product
$F(x) = cf_0(x)$ where $c \in \Q$ and $f_0(x)$ is a primitive polynomial on
$\Z[x]$. Moreover, $f(x) \in \Z[x]$ if and only if $c \in \Z$. If so, then
$|c|$ is the greatest common divisor of the coefficients of $f(x)$ and the sign
of $c$ is the sign of the leading coefficient of $f(x)$.
\end{lemma*}
\begin{theorem*}[Gauss' Lemma for {$\Z[x]$}] \label{gauss}
Let $f(x) \in \Z[x]$ be non-constant. If $f(x)$ is irreducible in $\Z[x]$, then
it is irreducible in $\Q[x]$. 
\end{theorem*}
\begin{example}
The converse of \cref{gauss} is not true. Consider the polynomial $2x + 8$ is
irreducible in $\Q[x]$, but $2x+8 = 2(x+4)$ is reducible in $\Z[x]$.
\end{example}
\begin{remark}
$f(x) \in \Z[x]$  is irreducible in $\Z[x]$ if and only if either
\begin{enumerate}
\item $f(x)$ is a prime integer
\item $f(x)$ is a primitive polynomial which is irreducible in $\Q[x]$
\end{enumerate}
\end{remark}
\begin{theorem}[Eisenstein's Criterion for {$\Z[x]$}] \label{eisenstien}
Let $f(x) = a_nx^n + \dots + a_1x + a_0 \in \Z[x]$ and let $p$ be a prime
integer. Suppose that $p \nmid a_n$, $p \mid a_i$ for all $0 \leq i \leq (n-1)$
and $p^2 \nmid a_0$, then $f(x)$ is irreducible in $\Q[x]$. In particular, if
$f(x)$ is primitive, then it is irreducible in $\Z[x]$.
\end{theorem}
\begin{proof}
Consider the map $f: \Z[x] \to \Z_p[x]$ defined by
\begin{equation*}
f(x) \mapsto \bar f(x) = \bar a_nx^n + \dots + \bar a_1x + \bar a_0
\end{equation*}
where $\bar a_i = a_i \Mod{p} \in \Z_p$. Since $p \nmid a_n$ and $p \mid a_i$
for all $0 \leq i (n-1)$, we have $\bar f(x) = \bar a_nx^n$ with $\bar a_n \neq
0$. If $f(x)$ is reducible in $\Q[x]$, then it can be factored in $\Z[x]$ into
polynomials of positive degree, say $f(x) = g(x)h(x)$ with $g(x), h(x) \in
\Z[x]$ and $\deg(g), \deg(h) \geq 1$. It follows that $\bar a_nx^n = \bar
g(x) \bar h(x)$ from which we see that $\bar g(x)$ and $\bar h(x)$ have no
constant terms in $\Z_p[x]$, as $\Z_p[x]$ is a UFD\@. Since the constants of
both $g(x)$
and $h(x)$ are divisible by $p$, this implies that the constant of $f(x)$ is
divisible by $p^{2}$, which leads to a contradiction. So, $f(x)$ is irreducible
in $\Q[x]$
\end{proof}
\begin{example}
The polynomial $2x^7 + 3x^4 + 6x^2 + 12$ is irreducible in $\Q[x]$ by applying
Eisenstein's Criterion with $p=3$.
\end{example}
\begin{example}
Consider the \underline{$n^{\text{th}}$ cyclotomic polynomial} defined by
\begin{equation*}
\Phi_n(x) = \sum_{\substack{1 \leq k \leq n\\\gcd(k,n) = 1}}
\bigg(x-e^{2i\pi\frac{k}{n}} \bigg).
\end{equation*}
If $n = p$ where $p$ is a prime number, then $\xi_p = e^{\frac{2i\pi}{p}} =
\cos{\frac{2\pi}{p}} + i\sin{\frac{2\pi}{p}}$ (the $p^{\text{th}}$ root of 1)
is a root of the $p^{\text{th}}$ cyclotomic polynomial. Notice here, since $p$
is co-prime with all $1 \leq k \leq p$, we have
\begin{equation*}
\Phi_p(x) = x^{p-i} + x^{p-2} + \dots + x + 1 = \frac{x^p -1}{x-1}
\end{equation*}
Eisenstein's Criterion does not imply the irreducibility of $\Phi_p(x)$
immediately; however, consider
\begin{equation*}
\Phi_p(x+1) = \frac{(x+1)^p -1}{x} = x^{p-1} + \binom{p}{1}x^{p-2} + \dots +
\binom{p}{p-2}x + \binom{p}{p-1}\in \Z[x]
\end{equation*}
with the Binomial Theorem. Since $p$ is prime, $p \nmid 1$, $p \mid
\binom{p}{i}, \forall i \in \{1,\dots,p-1\}$ and $p^2 \nmid \binom{p}{p-1}$.
Here, Eisenstein's Criterion gives that $\Phi_p(x+1)$ is irreducible in
$\Q[x]$, but if $\Phi_p(x) = g(x)f(x)$, then $\Phi_p(x+1) = g(x+1)h(x+1)$ gives
a factorization for $\Phi_p(x+1)$, so $\Phi_p(x)$ must be irreducible in
$\Q[x]$ as well. Furthermore, since $\Phi_p(x)$ is primitive, $\Phi_p(x)$ is
also irreducible in $\Z[x]$.
\end{example}
\begin{example}
Let $p$ be prime and $\xi_p = e^{\frac{2i\pi}{p}}$. Since it is a root of
$\Phi_p(x)$, which is irreducible, by \cref{theorem4},
\begin{equation*}
[\Q(\xi_p):\Q] = \deg(\Phi_p(x)) = p-1.
\end{equation*}
The field $\Q(\xi_p)$ is called the \underline{$p^{\text{th}}$ cyclotomic
extension on $\Q$}.
\end{example}
\begin{example}
Let $\bar\Q$ be the algebraic closure of $\Q$ in $\C$. Since $\xi_p \in \Q$, we
have
\begin{equation*}
[\bar\Q : \Q] \geq [\Q(\xi_p):\Q] = p-1.
\end{equation*}
Since $p \to \infty$, we have $[\bar\Q:\Q]$ is $\infty$. We have seen in
\cref{theorem6} that if $\quotient{E}{F}$ is finite, then $\quotient{E}{F}$ is
algebraic. However, this example shows that the converse is false. 
\end{example}
\sectionline
Now, let $R$ be any unique factorization domain and let $F$ be it's fraction
field. Then $R[x]$ is a subring of $F[x]$.
\begin{lemma*} [Gauss' Lemma]
Let $R$ be a UFD with the fraction field $F$. Let $f(x) \in R[x]$ be
non-constant. If $f(x)$ is irreducible in $R[x]$, then it is irreducible in
$F[x]$.
\end{lemma*}
\begin{theorem} [Eisenstein's Criterion]
Let $R$ be a UFD with the fraction field $F$. Let $\ell$ be an irreducible
element of $R$. If $f(x) = a_nx^n + \dots + a_1x + a_0 \in R[x]$ with $n \geq
1$, $\ell \nmid a_n$, $\ell \mid a_i$, for all $0 \leq i \neq (n-1)$ and
$\ell^2 \nmid a_0$, then $f(x)$ is irreducible in $F[x]$.
\end{theorem}

\pagebreak
\section{Splitting Fields}
\begin{definition}
Let $\quotient{E}{F}$ be a field extension. We say $f(x) \in R[x]$
\underline{splits over $E$} if $E$ contains all roots of $f(x)$. In other words,
$f(x)$ is a product of linear factors in $E[x]$.
\end{definition}
\begin{definition}
Let $\quotient{\tilde{E}}{F}$, $f(x) \in F[x]$ and $F \subseteq E \subseteq
\tilde E$. If
\begin{enumerate}
\item $f(x)$ splits over $E$
\item there is no proper subfield of $E$ such that $f(x)$ splits over $E$, 
\end{enumerate}
Then we say $E$ is a \underline{splitting field of $f(x) \in F[x]$ in $\tilde
E$}.
\end{definition}

\subsection{Existence of Splitting Fields}
\begin{theorem}
Let $p(x) \in F[x]$ be irreducible. The quotient ring
$\quotient{F[x]}{\cyclic{p(x)}}$ is a field containing $F$ and a root of
$p(x)$.
\label{theorem10}
\end{theorem}
\begin{proof}
Since $p(x)$ is irreducible, the ideal $I = \cyclic{p(x)}$ is maximal. Thus,
$E = \quotient{F[x]}{I}$ is a field. Consider the map
\begin{equation*}
\Psi:F\to E, \quad a \mapsto a + I
\end{equation*}
Since $F$ is a field and $\Psi \neq 0$, $\Psi$ is injective. Thus, be
identifying $F$ with $\Psi(F)$, $F$ is a subfield of $E$.
\begin{claim}
Let $\alpha = x + I \in E$. Then $\alpha$ is a root of $p(x)$.
\end{claim}
Notice,
\begin{align*}
p(x) &= a_0 + a_1x + \dots + a_nx^n\\
&= (a_0 + I) + (a_1 + I)x + \dots (a_n + I)x^n\\
&\in E[x].
\end{align*}
Thus, we have
\begin{align*}
p(\alpha) &= (a_0 + I) + (a_1 + I)\alpha + \dots + (a_n + I)\alpha^n\\
&= (a_0 + I) + (a_1 + I)(x+I) + \dots + (a_n + I)(x+I)^n\\
&= (a_0 + a_1x + \dots + a_nx^n) + I \tag{since $(x+I)^i = x^i + I$}\\
&= p(x) + I\\
&= 0 + I\\
&= I
\end{align*}
Thus, $\alpha = x+I \in E$ is a root of $p(x)$.
\end{proof}
\begin{theorem} [Kronecker]
Let $f(x) \in F[x]$. There exists a field $E$ containing $F$ such that
$f(x)$ splits over $E$.
\label{theorem11}
\end{theorem}
\begin{proof}
We proceed with induction on $\deg(f)$. If $\deg(f) = 1$, let $E=F$ and we are
done. Suppose $\deg(f)>1$ and the statement holds for all $g(x)$ with
$\deg(g) > \deg(f)$ ($g(x)$ need not to be in $F[x]$). We write $f(x) =
p(x)h(x)$, where $p(x),h(x) \in F[x]$ and $p(x)$ is irreducible. By
\cref{theorem10}, there exists a field $K$ such that $F \subseteq K$ and $K$
containing a root of $p(x)$, say $\alpha$. Thus, $p(x) = (x-\alpha)q(x)$ and
$f(x) = (x-\alpha)g(x)h(x)$ where $q(x) \in K[x]$. Since $\deg(hq) <
\deg(f)$, by induction, there exists a field $E$ containing $K$ over which
$h(x)q(x)$ splits. It follows that $f(x)$ splits over $E$. 
\end{proof}
\begin{theorem}
Every $f(x) \in F[x]$ has a splitting field, which is a finite extension of $F$.
\label{theorem12}
\end{theorem}
\begin{proof}
For $f(x) \in F[x]$, by \cref{theorem11}, there exists a field extension
$\quotient{E}{F}$ over which $f(x)$ splits, say $\alpha_1, \alpha_2, \dots, a_n$
are roots of $f(x) \in E$. Consider $F(\alpha_1,\dots,\alpha_n)$. The field
contains all the roots of $f(x)$ and $f(x)$ does not split over any proper
subfield of it. Thus, $F(\alpha_1,\dots,\alpha_n)$ is the splitting field of
$f(x)$ in $E$. In addition, since $\alpha_i$ are all algebraic,
$\quotient{F(\alpha_1,\dots,\alpha_n)}{F}$ is finite.
\end{proof}

\subsection{Uniqueness of Splitting Fields}
We have seen from \cref{theorem12} that for a field extension $\quotient{\tilde
E}{F}$, a splitting field of $f(x) \in F[x]$ in $E$ is of the form
$F(\alpha_1,\dots,\alpha_n)$ where $\alpha_i$ are roots of $f(x)$ in $\tilde E$.
Thus, it is unique within $\tilde E$.\\

If we change $\quotient{E}{F}$ to a different field extension, sat
$\quotient{E'}{F}$, what is the relation between the splitting field of $f(x)$
in $E$ and the one in $E'$?
\begin{definition}
Let $\phi:R\to R'$ be a ring homomorphism, and $\Phi: R[x] \to R'[x]$ be the
unique ring homomorphism satisfying $\Phi \big|_R = \emptyset$ and $\Phi(x) =
x$. In this case, we say \underline{$\Phi$ extends $\phi$}. More generally, if
$R \subseteq S$, $R' \subseteq S'$, and $\Phi: S \to S'$ is a ring homomorphism
with $\Phi \big|_R = \emptyset$, we say \underline{$\Phi$ extends $\phi$}.
\end{definition}
\begin{theorem}
Let $\phi:F \to F'$ be an isomorphism of fields and $f(x) \in F[x]$. Let
$\Phi: F[x] \to F'[x]$ be the unique ring homomorphism which extends $\phi$. Let
$f'(x) = \Phi(f(x))$ and $\quotient{E}{F}$ and $\quotient{E'}{F'}$ be splitting
fields of $f(x)$ and $f'(x)$ respectively. Then there exists an isomorphism
$\Psi:E\to E'$.
\label{theorem13}
\end{theorem}
\begin{proof}
We proceed with induction on $[E:F]$. If $[E:F] = 1$, then $f(x)$ is a product
of linear factors in $F[x]$, and so is $f'(x)$ in $F'[x]$. Thus, $E = F$ and
$E' = F'$ so take $\Psi = \phi$ and we are done. Now, suppose $[E:F] < 1$ and
the statement is true for all field extensions $\quotient{\tilde E}{\tilde F}$
with $[\tilde E: \tilde F]<[E:F]$. Let $p(x) \in F[x]$ be an irreducible factor
of $f(x)$ with $\deg(p)>1$ and let $p'(x) = \Phi(f(x))$ (such $p(x)$ exists as
if all irreducible factors of $f(x)$ are of degree 1, then $[E:F] = 1$). Let
$\alpha \in E$ and $\alpha' \in E'$ be roots of $p(x)$ and $p'(x)$ respectively.
From \cref{theorem3}, we have an $F$-isomorphism,
\begin{equation*}
F(\alpha) \cong \quotient{F[x]}{\cyclic{p(x)}}, \quad \alpha \mapsto x +
\cyclic{p(x)}
\end{equation*}
Similarly, there is an $F'$-isomorphism,
\begin{equation*}
F'(\alpha) \cong \quotient{F'[x]}{\cyclic{p'(x)}}, \quad \alpha \mapsto x +
\cyclic{p'(x)}
\end{equation*}
Consider the isomorphism $\Phi:F[x] \to F'[x]$ which extends $\phi$. Since
$p'(x) = \Phi(f(x))$, there exists a field isomorphism,
\begin{equation*}
\tilde\Phi: \quotient{F[x]}{\cyclic{p(x)}} \to \quotient{F'[x]}{\cyclic{p'(x)}},
\quad x + \cyclic{p(x)} \mapsto  x + \cyclic{p'(x)}
\end{equation*}
which extends $\phi$. It follows that there exists a field isomorphism,
\begin{equation*}
\tilde\phi: F(\alpha) \to F'(\alpha), \quad \alpha \mapsto \alpha'
\end{equation*}
which extends $\phi$. Note that since $\deg(p) \geq 2$, $[E:F[\alpha]] < [E:F]$.
Since $E$ (respectively $E'$) is the splitting field of $f(x) \in
F(\alpha)[x]$ (respectively $f(x) \in F(\alpha)[x]$) over $F(\alpha)$
(respectively $F'(\alpha')$), by induction, there exists $\Psi:E \to E'$ which
extends $\tilde \phi$. Thus, $\Psi$ extends $\phi$.
\end{proof}
\begin{corollary}\label{corollary14}
Any two splitting fields of $f(x) \in F[x]$ over $F$ are $F$-isomorphic. Thus,
we say ``the'' splitting field of $f(x)$ over $F$.
\end{corollary}
\begin{proof}
Let $\phi:F \to F$ be the identity map and apply \cref{theorem13}
\end{proof}

\subsection{Degree of Splitting Fields}

\begin{theorem}
If $\quotient{E}{F}$ is the splitting field of $f(x)$, then $[E:F] \mid
\deg(f)\fact$.
\label{theorem14}
\end{theorem}
\begin{proof}
We proceed by induction on $\deg(f)$. If $\deg(f) = 1$, choose $E = F$ and we
have $[E:F] \mid 1$. Suppose $\deg(f) < 1$ and the statement holds for all
$g(x)$ with $\deg(g) < \deg(f)$. We break this down into two cases.\\
\underline{\bf Case 1}: If $f(x) \in F[x]$ is irreducible and $\alpha \in E$ is
a root of $f(x)$, by \cref{theorem13},
\begin{equation*}
F(\alpha) \cong \quotient{F[x]}{\cyclic{f(x)}} \quad \text{and} [F(\alpha):F] =
\deg(f) = n.
\end{equation*}
We write $f(x) = (x-\alpha)g(x) \in F(\alpha)[x]$ with $g(x) \in
F(\alpha)[x]$. Since $E$ is the splitting field of $g(x)$ over $F[\alpha]$ and
$\deg(g) = n$, by induction hypothesis, $[E:F(\alpha)] \mid (n-1)\fact$. Since
$[E:F] = [E:F(\alpha)][F(\alpha):F]$, it follows that $[E:F] \mid n\fact$.\\
\underline{\bf Case 2}: If $f(x)$ is not irreducible, write $f(x) = g(x)h(x)$
with $g(x),h(x) \in F[x]$, $\deg(g)=m, \deg(h) = k$, $1 \leq m,k, < n$ and
$m + k = n$. Let $K$ be the splitting field of $g(x)$ over $F$. Since $\deg(g) =
m$, by induction, $[K:F] \mid m\fact$. Since $E$ is the splitting field of
$h(x)$ over $K$ and $\deg(h) = k$, by induction hypothesis, $[E:K] \mid k\fact$.
Thus, $[E:F] \mid m\fact k\fact$, which is a factor of $n\fact$ as
\begin{equation*}
\frac{n\fact}{m \fact k\fact} = \binom{n}{m} \in \Z
\end{equation*}
\end{proof}

\pagebreak
\section{Finite Fields}
\subsection{Prime Fields}
\begin{definition}
The \underline{prime field} of a field $F$ is the intersection of all subfields
of $F$.
\end{definition}
\begin{theorem}
If $F$ is a field, then its prime field is isomorphic to either $\Q$ or $\Z_p
\coloneqq \quotient{\Z}{p\Z}$ for some prime $p$.
\label{theorem16}
\end{theorem}
\begin{proof}
Consider the ring map $\chi:\Z \to F$ defined by
\begin{equation*}
\chi(n) = n\cdot 1 = \underbrace{1 + \dots + 1}_{n\,\text{times}}
\end{equation*}
Let $I = \ker(\chi)$, the kernel of $\chi$. Since $\quotient{\Z}{I} \cong
\im(\chi)$, a subring of $F$, it is an integral domain. Thus, $I$ is a prime
ideal. We break this down to two cases.\\
\underline{Case 1}: If $I = \cyclic{0}$, then $\Z \subseteq F$. Since $F$ is a
field, $\Q = \Frac(\Z) \subseteq F$.\\
\underline{Case 2}: If $I = \cyclic{p}$, then
\begin{equation*}
\Z_p = \quotient{\Z}{p\Z} \cong \im{\chi} \subseteq F
\end{equation*}
\end{proof}
\begin{definition}
Given a field $F$, if its prime field is isomorphic to $\Q$ (respectively
$\Z_p$), we say $F$ has \underline{characteristic 0} (respectively
characteristic $p$) denoted by $\ch(F) = 0$ (respectively $\ch(F) = p$).
\end{definition}
\begin{remark}
Note that if $\ch(F) = p$, for $a,b, \in F$,
\begin{equation*}
(a+b)^p = a^p + b^p.
\end{equation*}
Using this property, the following proposition follows.
\end{remark}
\begin{prop}
Let $F$ be a field with $\ch(F) = p$ and let $n\in\N$. Then, the map $\phi:F \to
F$ given by $u \mapsto u^{p^n}$ is an injective $\Z_p$-homomorphism of fields.
If $F$ is finite, then $\phi$ is a $\Z_p$-isomorphism of $F$.
\end{prop}

\subsection{Formal Derivatives and Repeated Roots}
\begin{definition}
If $F$ is a field, the monomials $\{1, x, x^2, \dots\}$ for a $F$-basis of
$F[x]$. Define the linear operator
\begin{equation*}
D:F[x] \to F[x]
\end{equation*}
by $D(1) = 0$ and $D(x^i) = ix^{i-1}$ for all $i \in \N$. Thus for
\begin{equation*}
f(x) = a_0 + a_1x + \dots + a_nx^n, a_i \in F
\end{equation*}
we have
\begin{equation*}
D(f)(x) = a_1 + 2a_2x + \dots + na_nx^{n-1}.
\end{equation*}
Note that
\begin{enumerate}
\item $D$ is linear: $D(f+g) = D(f) + D(g)$
\item $D$ respects the Leibniz Rule: $D(fg) = \big(D(f)\big)g +
f\big(D(g)\big)$.
\end{enumerate}
We call $D(f) = f'$ the \underline{formal derivative} of $f$.
\end{definition}
\begin{theorem}
Let $F$ be a field and $f(x) \in F[x]$.
\begin{enumerate}
\item If $\ch(F) = 0$, then $f'(x) = 0$ if and only if $f(x) = c$ for some $c
\in F$.
\item If $\ch(F) = p$, then $f'(x) = 0$ if and only if $f(x) = g(x^p)$ for some
$g(x) \in F[x]$
\end{enumerate}
\label{theorem18}
\end{theorem}
\begin{proof}\leavevmode
\begin{enumerate}
\item Backwards is trivial. Suppose we have $f(x) = a_0 + a_1x + \dots +
a_nx^n$, then $f'(x) = a_1 + 2a_2x + \dots + na_nx^{n-1} = 0$. This implies that
$ia_i = 0$ for all $1 \leq i \leq n$, Since $\ch(F) = 0$, $i \neq 0$. Thus,
$a_i = 0$ for all $i \geq 1$. This, $f(x) = a_0 \in F$.
\item 
\underline{Forwards}. For $f(x) = a_0 + a_1x + \dots + a_nx^n$, $f'(x) = a_1 +
2a_2x + \dots + na_nx^{x-1} = 0$ implies that $ia_i = 0$ for all $1 \leq i \leq
n$. Since $\ch(F) = p$, $ia_i = 0$ implies that $ia_i = 0$ implies that
$a_i = 0$ unless $p \mid i$. Thus,
\begin{equation*}
f(x) = a_0 + a_px^p + \dots a_{mp}x^{mp} = g(x^p)
\end{equation*}
where $g(x) = a_0 + a_p + \dots +a_{mp}x^m \in F[x]$.\\
\underline{Backwards}. Write $g(x) = b_0 + b_1x + \dots + b_mx^m \in
F[x]$. Then,
\begin{equation*}
f(x) = g(x^p) = b_0 + b_1x^p + \dots + b_mx^{mp}.
\end{equation*}
Thus, $f'(x) = pb_1x^{p-1} + 2pb_2x^{2p-1} + \dots + mpb_m^{pm-1}$. Since
$ch(F) = p$, we have $f'(x) = 0$.
\end{enumerate}
\end{proof}
\begin{definition}
Let $\quotient{E}{F}$ is a field extension and $f(x) \in F[x]$. We say
$\alpha \in E$ is a \underline{repeated root} of $f(x)$ if $f(x) =
(x-\alpha)^2g(x)$ for some $g(x) \in E[x]$.
\end{definition}
\begin{theorem}
Let $\quotient{E}{F}$ is a field extension and $f(x) \in F[x]$. Then $\alpha$ is
a repeated root of $f(x)$ if and only if $(x -\alpha)$ divides both $f$ and
$f'$. In other words, $(x - \alpha) \mid \gcd(f,f')$.
\label{theorem19}
\end{theorem}
\begin{proof}
\underline{Forwards}. Suppose $f(x) = (x-\alpha)^2g(x)$. Then,
\begin{align*}
f'(x) &= 2(x-\alpha)g(x) + (x-\alpha)^2g'(x)\\
&= (x-a) \big(2g(x) + (x-\alpha)g'(x) \big)
\end{align*}
Thus, $(x-\alpha)$ divides both $f$ and $f'$.\\
\underline{Backwards}. Suppose $(x-\alpha)$ divides both $f$ and $f'$. We write
$f(x) = (x-\alpha)h(x)$ where $h(x) \in E[x]$. Then, $f'(x) = h(x) +
(x-\alpha)h'(x)$. Since $f'(\alpha) = 0$, we have $h(\alpha) = 0$. Thus,
$(x-\alpha)$ is a factor of $h(x)$ and $f(x) = (x-\alpha)^2g(x)$ for some
$g(x) \in E[x]$.
\end{proof}
\begin{corollary}
Let $F$ be a field and $f(x) \in F[x]$. Then $f(x)$ has no repeated roots if and
only if $\gcd(f, f') = 1$.
\label{corollary20}
\end{corollary}

\subsection{Finite Fields}
\begin{prop}
If $F$ is a finite field, then $\ch(F) = p \neq 0$ for some prime $p$ and $|F| =
p^n$ for some $n \in \N$. 
\end{prop}
\begin{proof}
Since $F$ is a finite field, by \cref{theorem16}, its prime field is $\Z_p$.
Since $F$ is a finite dimensional vector space over $\Z_p$, we have
\begin{equation*}
F \cong \underbrace{\Z_p \times \dots \times \Z_p}_{n\>\text{summands}}.
\end{equation*}
Thus $|F| = p^n$.
\end{proof}
\begin{theorem}
Let $F$ be a field and $F^* = F\setminus\{0\}$, multiplicative group of nonzero
elements of $F$. Let $G$ be a finite subgroup of $F^*$, then $G$ is a cyclic
group. In particular, if $F$ is a finite field, then $F^*$ is a cyclic group.
\label{theorem21}
\end{theorem}
\begin{proof}
If $G = \cyclic{1}$, the result follows immediately. Otherwise, since $G$ is a
finite abelian group,
\begin{equation*}
G \cong \quotient{\Z}{n_1\Z} \times \dots \times \quotient{\Z}{n_r\Z}
\end{equation*}
where $n_i > 1$ and $n_1 \mid \dots \mid n_r$. Since
$n_r\left(\quotient{\Z}{n_1\Z} \times \dots \times \quotient{\Z}{n_r\Z}\right) =
0$, it follows that every $u \in G$ is a root of $x^{n_r} - 1 \in F[x]$. Since
the polynomial has at most $n_r$ distinct roots in $F$, we have $r = 1$ and
$G \cong \quotient{\Z}{n_r\Z}$.
\end{proof}
By taking $u$ to be a generator of the multiplicative group $F^*$, we have the
following corollary.
\begin{corollary}
f $F$ is a finite field, then $F$ is a simple extension of $\Z_p$. In other
words, $F = \Z_p(u)$ for some $u \in F$.
\end{corollary}
\begin{prop} \label{prop24}
Let $p$ be prime and $n \in \N$. Then $F$ is a finite field with $|F| = p^n$ if
and only if $F$ is a splitting field of $x^{p^n} - x$ over $\Z_p$.
\end{prop}
\begin{proof}
\underline{Forwards}: If $|F| = p^n$, then $|F^*|= p^n - 1$. Thus, every $u \in
F$ satisfies $u^{p^n-1} = 1$ and thus is a root of $x(x^{p^n-1} - 1) =
x^{p^n} - x \in \Z_p[x]$. Since $0 \in F$ is also a root of $x^{p^n} - x$, the
polynomial $x^{p^n} - x$ has distinct $p^n$ distinct roots in $F$. In other
words, it splits over $F$. Thus $F$ is a splitting field of $x^{p^n} - x$ over
$\Z_p$.\\
\underline{Backwards}: Suppose $F$ is a splitting field of $f(x) = x^{p^n} - x$
over $\Z_p$. Since $\ch(F) = p$, we have
\begin{align*}
f'(x) &= p^nx^{p^n-1} - 1\\
&\equiv -1 \Mod{p}.
\end{align*}
Now, since $\gcd(f,f') = 1$, by \cref{corollary20}, $f(x)$ has $p^n$ distinct
roots in $F$. Let $E$ be the set of the roots of $f(x)$ in $F$. Let $\varphi:F
\to F$ be given by $u \mapsto u^{p^n}$. For $u \in F$, $u$ is a root of $f(x)$
if and only if $\varphi(u) = u$. Thus, the set $E$ is a subfield of $F$ of order
$p^n$ which contains $\Z_p$. Since $F$ is a splitting field, it is generated
over $\Z_p$ by the roots of $f(x)$, in other words, the elements of $E$. Thus,
$F = \Z_p(E) = E$.
\end{proof}
As a direct consequence of \cref{prop24} and \cref{corollary14}, we have the
following corollary.
\begin{corollary}[E. H. Moore]
Let $p$ be a prime and $n \in \N$. Then any two finite field of order $p^n$ are
isomorphic.
\label{corollary25}
\end{corollary}

\subsection{Separable Polynomials}
\begin{definition}
Let $F$ be a field and $f(x) \in F[x]$, $f \neq 0$. If $f(x)$ is irreducible, we
say $f(x)$ is \underline{separable over $F$} if it has no repeated root in any
extension $E$ of $F$. In the general case, we say $f(x)$ is \underline{separable
over $F$} if each irreducible factor of $f$ is separable over $F$.
\end{definition}
\begin{example}
$f(x) = (x-2)^2$ is separable over $\Q$.
\end{example}
\begin{example}
Consider the polynomial $f(x) = x^n - a \in F[x]$ with $n \geq 2$. We recall
that if $\gcd(f, f') = 1$, then $f(x)$ has no repeated root in any extension of
$F$. In other words, $f(x)$ is separable. Note that if $a = 0$, the only
irreducible factor of $f(x)$ is $x$ and $\gcd(x, 1) = 1$. Thus, $f(x)$ is
separable. Now, assume $a \neq 0$. Note that $f'(x) = nx^{n-1}$.
\begin{enumerate}
\item If $\ch(F) = 0$, we have $\gcd(f,f') = 1$ since
\begin{align*}
1 &= \frac{x}{na}nx^{n-1} - \frac{1}{a}(x^n-a)\\
&= \frac{x}{na}f' - \frac{1}{a}f
\end{align*}
Thus, $f$ is separable.
\item If $\ch(F) = p$ and $\gcd(n,p)$, then by Fermat's Little Theorem, $f(x) =
x - a$ and $f'(x) = 1$ so $\gcd(f,f') = 1$ and $f(x)$ is separable.
\item If $\ch(F) = p$ and $\gcd(n,p) \neq 1$, consider $f(x) = x^p - a$. Since
$f'(x) = px^{p-1} = 0$, we have $\gcd(f,f') \neq 1$. However, it is still
possible that all irreducible factors $\ell(x)$ of $f(x)$ has the property that
$\gcd(\ell, \ell') = 1$. To decide if $f(x)$ is separable, we need to find its
irreducible factors first. Define
\begin{equation*}
F^p \coloneqq \{b^p : b \in F\}
\end{equation*}
which is a subfield of $F$.
\begin{enumerate}
\item If $a \in F^p$, say $a = b^p$ for some $b \in F$, then
\begin{equation*}
f(x) = x^p - b^p = (x-b)^p \tag{by Binomial Theorem}
\end{equation*}
which is irreducible. Since each irreducible factor of $f(x)$ is linear, thus
separable. Thus, $f(x)$ is separable.
\item Suppose $a \not\in F$
\begin{claim}
$f(x) = x^p -a$ is irreducible in $F[x]$.
\end{claim}
We write $x^p - a = g(x)h(x)$ where $g(x),h(x) \in F[x]$ are monic polynomials.
Let $\quotient{E}{F}$ be an extension where $x^p - a$ has a root, say $\beta \in
E$ (i.e. $\beta^p - a = 0$). Note that $\beta \not\in F$, otherwise $a = b^p \in
F^p$. We have
\begin{equation*}
x^p -a = x^p - \beta^p = (x - \beta)^p. \tag{by Binomial Theorem}
\end{equation*}
Thus, $g(x) = (x - \beta)^r$ and $h(x) = (x - \beta)^s$ for some $r,s \in \N
\cup \{0\}$ and $r+s = p$. We write,
\begin{equation*}
g(x) = x^r - r\beta x^{r-1} + \dots
\end{equation*}
then $r\beta \in F$. Since $\beta \not\in F$, as an element of $F$, we have $r =
0$. Thus, as an integer, we have $r = 0$ or $r = p$. It follows that wither
$g(x) = 1$ or $h(x) = 1$ in $F[x]$. Thus, $f(x)$ is irreducible.\\

Since $f(x)$ is irreducible and $f(x) = (x-\beta)^p \in E[x]$, it is not
separable. This type of polynomial is called a \underline{purely inseparable
polynomial}.
\end{enumerate}
\end{enumerate}
\end{example}
\begin{definition}
A field $F$ is \underline{perfect} if every irreducible polynomial $r(x) \in
F[x]$ is separable over $F$.
\end{definition}
\begin{theorem}
Let $F$ be a field.
\begin{enumerate}
\item If $\ch(F) = 0$, then $F$ is perfect.
\item If $\ch(F) = p$ and $F = F^p$, then $F$ is perfect.
\end{enumerate}
\label{theorem26}
\end{theorem}
\begin{proof}
Let $r(x) \in F[x]$ be irreducible. Then
\begin{equation*}
\gcd(r,r') =
\begin{cases}
1 & \text{, if $r' \neq 0$}\\
0 & \text{, if $r' = 0$}
\end{cases}.
\end{equation*}
Suppose $r(x)$ is not separable. Then by \cref{corollary20}, $\gcd(r,r') \neq
1$, so it must be that $\gcd(r,r') = 0$.
\begin{enumerate}
\item If $\ch(F) = 0$, from \cref{theorem18}, $r'(x) = 0$ implis that $r(x) = c
\in F$, which is a contradiction since $\deg(r) \geq 1$. Thus, $r(x)$ is
separable and $F$ is perfect.
\item If $\ch = p$, from \cref{theorem18}, $r'(x) = 0$ implies that
\begin{equation*}
r(x) = a_0 + a_1x^p + a_2x^{2p} + \dots + a_mx^{mp}, a_i \in F
\end{equation*}
Since $F = F^p$, we can write $a_i = b_i^p$ with $b_i \in F$. Thus,
\begin{align*}
r(x) &= b_0^p + b^p_1x^p + b^p_2x^{2p} + \dots + b^p_mx^{mp}\\
&= (b_0 + b_1x + b_2x^2 + \dots + b_mx^m)^p
\end{align*}
which raises a contradiction since $r(x)$ is irreducible. Thus, $r(x)$ must be
separable and $F$ is perfect.
\end{enumerate}
\end{proof}
\begin{remark}
Let $\ch(F) = p$ and $F \neq F^p$ (e.g. $F = \mathbb{F}_p(x)$). If we take
$a \in \quotient{F}{F_p}$, then the polynomial $x^p -a$ is not separable. Thus,
if $\ch(F) = p$, $F$ is perfect if and only if $F^p=F$.
\end{remark}
\begin{corollary}
Every finite field is perfect.
\label{corollary27}
\end{corollary}
\begin{proof}
Every finite field $F$ with $|F|=p^n$ is the splitting field of $x^{p^n} - x$
over $\Z_p$ for some prime $p$ and $n \in \N$. Thus, for every $a \in F$,
$a = a^{p^n} = (a^{p^{n-1}})^p$. Since $a^{p^{n-1}} \in F$, $F = F^p$. Thus, by
\cref{theorem26}, $F$ is perfect.
\end{proof}
\begin{remark}
It is possible that $F^p = F$ and $F$ is an infinite field, say $F =
\bar{\mathbb{F}_p}$.
\end{remark}

\pagebreak
\section{The Sylow Theorems}
Recall the following definitions and theorems from Group Theory:
\begin{theorem*}[Lagrange's Theorem]
If $H$ is a subgroup of a group $G$, then $|G| = [G:H]|H|$. In particular, if
$G$ is finite, and $g\in G$, then $|\cyclic{g}|$ divides $|G|$.
\end{theorem*}
We can ask the reverse question; if a positive integer $m$ divides the order of
a group $G$, does $G$ have a subgroup of order $m$?
\begin{definition}
An \underline{action} of a group $G$ on a set $S$ is a function $G\times S \to
S$ (usually denoted by $(g,x) \mapsto gx$ such that for all $x \in S$ and $q_1,
g,2 \in G$, we have $ex = x$ and $(g_1g_2)x = g_1(g_2x)$). We say $G$ acts on
$S$ by a group action.
\end{definition}
\begin{definition}
If $G$ acts on $S$, for $x \in S$, we define the \underline{orbit} of $x$ by
$\bar x \coloneqq \{gx : g \in G\}$.
\end{definition}
\begin{definition}
If $G$ acts on $S$, for $x \in S$, we define the \underline{stabilizer} of $x$
by $G_x \coloneqq {g \in G : gx = x}$. $G_x$ is a subgroup of $G$ and $|\bar x|
= [G:G_x]$.
\end{definition}
\begin{definition}
Let $G$ be a group acting on itself by conjugation. Then, for $x \in G$, we
define the \underline{centralizer} of $x$ by $C_G(x) \coloneqq G_x = \{g\in G:
gxg^{-1} = x$.
\end{definition}
\begin{definition}
Let $S$ be all subgroups of $G$ and let $G$ act on $S$ by conjugation. Then, for
$K \in S$, we define the \underline{normalizer} of $K$ by $N_G(K) \coloneqq G_K
= {g \in G:gKg^{-1} = K}$.
\end{definition}
\begin{definition}
Let $G$ be a group. Then we define the \underline{center} of $G$ by $C(G)
\coloneqq \{g \in G:gxg^{-1} = x, \forall x \in G\}$.
\end{definition}
\begin{theorem*}[Class Equation of a Group]
Suppose $G$ is a finite group acting on itself by conjugation, $C(G)$ is the
center of $G$, and $C_1, C_2, \dots, C_r$ are all the conjugacy classes in $G$
comprising the elements outside the center. Let $g_i$ be an element in $C_i$ for
each $1 \leq i \leq r$. Then, we have
\begin{equation*}
|G| = |C(G)| + \sum^r_{i=1}|G:C_G(g_i)|.
\end{equation*}
\end{theorem*}
\begin{lemma}
Let $H$ be a group of order $p^n$ for some prime $p$, which acts on a finite set
$S$. Let $S_0 = \{ x \in S: hx = x, \forall h \in H\}$. Then, we have $|S|
\equiv |S_0| \Mod{p}$.
\label{lemma28}
\end{lemma}
\begin{proof}
For $x \in S$, $|\bar x| = 1$ if and only if $x \in S_0$. Thus, $S$ can be
written as a disjoint union $S = S_0 \cup \bar{x_1} \cup \dots \cup \bar{x_n}$.
Thus,
\begin{equation*}
|S| = |S_0| + \sum^n_{i=0} |\bar{x_i}|.
\end{equation*}
Since $|\bar{x_i}| > 1$ and $|\bar{x_i}| = [H:H_{x_i}]$ divides $|H| = p^n$, we
have $p \mid |\bar{x_i}|$ for all $i$. It follows that $|S| \equiv |S_0|
\Mod{p}$.
\end{proof}
\begin{theorem}
Let $p$ be prime and $G$ a finite group. If $p \mid |G|$, then $G$ contains an
element of order $p$.
\label{theorem29}
\end{theorem}
\begin{proof}
Consider the set,
\begin{equation*}
S = \{(a_1, \dots, a_p) : a_i \in G, a_1\cdots a_p = e\}.
\end{equation*}
Since $a_p$ is uniquely determined and $|G| = n$, we have$|S| = n^{p-1}$. Since
$p \mid n$, we have $|S| \equiv 0 \Mod{p}$. Let the group $\Z_p$ act on $S$ by
cyclic permutation, in other words, for $k \in \Z_p, k(a_1,\dots,a_p) =
(a_{k+1}, a_{k+2}, \dots, a_p, a_1, \dots, a_k)$. Since $(a_1, \dots, a_p) \in
S_0$ if and only if $a_1 = \dots = a_p$. Clearly, $(e,\dots, e) \in S_0$, so
$|S_0| \geq 1$. By \cref{lemma28}, we have $|S_0| \equiv |S| \equiv 0 \Mod{p}$.
So $|S_0| \geq p$. Thus, there exists $a \neq e$ such that $(a, \dots, a) \in
S_0$ which implies that $a^p = e$. Since $p$ is prime, the order of $a$ is $p$.
\end{proof}

\begin{definition}
Let $p$ be a prime. A group in which the order of every element is a
non-negative power of $p$ is called a $p$-group. 
\end{definition}
\begin{corollary}
A finite group $G$ is a $p$-group if and only if $|G|$ is a power of $p$.
\label{corollary30}
\end{corollary}
\begin{proof}
This is a direct consequence of \cref{theorem29}.
\end{proof}
\begin{lemma}
The center $C(G)$ of a nontrivial finite $p$-group $G$ contains more than 1
element.
\label{lemma31}
\end{lemma}
\begin{proof}
Since $G$ is a $p$-group by \cref{corollary30}, $|G|$ is a power of $p$. Recall
the class equation:
\begin{equation*}
|G|=|C(G)|+\sum_{i=1}^n[G:C_G(x_i)], \quad\text{where } [G:C_G(x_i)]\geq 1.
\end{equation*}
Since $|G|$ is a power of $p$, $[G:C_G(x_i)]\mid|G|$, and $[G:C_G(x_i)]>1$. We
see that $p \mid [G:C_G(x_i)]$. It follows that $p \mid |C(G)|$ since
$|C(G)|\geq1$ so $C(G)$ has at least $p$ elements.
\end{proof}
\begin{definition}
If $H$ is a subgroup of a group $G$, then the \underline{normalizer} of H is
defined by
\begin{equation*}
N_G(H) = \{g \in G:gHg^{-1} = H\}.
\end{equation*}
In particular, $H \triangleleft N_G(H)$.
\end{definition}
\begin{lemma}
If $p$ is prime and $H$ is a $p$-subgroup of a finite group $G$, then
$[N_G(H):H] \equiv [G:H] \Mod{p}$.
\label{lemma32}
\end{lemma}
\begin{proof}
Let $S$ be the set of all left cosets of $H$ in $G$ and let $H$ act on $S$ by
left translation, $G \times S \to S$ defined by,
\begin{equation*}
h\cdot xH \mapsto (hx)H
\end{equation*}
which fixes on coset to another. Then, $|S| = [G:H]$. For some fixed $x \in G$,
consider the set $S_0$ defined by $xH \in S_0 \iff hxH = xH$ for all $h \in H$.
In other words, all elements of $S_0$ are fixed by the group action. Now, we
have,
\begin{align*}
xH \in S_0 &\iff hxH = xH\\
&\iff x^{-1}hxH = H\\
&\iff x^{-1}Hx = H\\
&\iff x \in N_G(H)
\end{align*}
So, $|S_0| = [N_G(H):H]$. By \cref{lemma28},
\begin{align*}
[N_G(H):H] &= |S_0|\\
&\equiv |S| \Mod{p}\\
&= [G:H].
\end{align*}
\end{proof}
\begin{corollary}
If $H$ is a $p$-subgroup of a finite group $G$ such that $p \mid [G:H]$, then
$N_G(H) \neq H$.
\label{corollary33}
\end{corollary}
\begin{proof}
Since $p \mid [G:H]$, by \cref{lemma32} we have $[H_G(H):H] \equiv [G:H] \equiv
0 \Mod{p}$. Since $p \mid [N_G(H):H]$ and $[N_G(H):H] \geq 1$, we have
$[N_G(H):H] \geq p$, so $N_G(H) \neq H$.
\end{proof}
\begin{theorem}[First Sylow Theorem]
Let $G$ be a group with order $p^nm$ with $p$ prime, $n \geq 1$, $\gcd(p,m)=1$.
Then $G$ contains a subgroup of order $p^i$ for all $1 \leq i \leq n$ which is
normal under some subgroup of order $p^{i+1}$.
\label{fst}
\end{theorem}
\begin{proof}
We proceed with induction on $i$. For $i=1$, since $p \mid |G|$, we have be
\cref{theorem29} that $G$ contains an element $a$ of order $p$, so
$|\cyclic{a}| = p$. Suppose that the statement holds for some $1 \leq i \leq n$,
say $H$ is a subgroup of order $p^i$. Now, from \cref{corollary33}, we have
$p \mid [N_G(H):H]$ and $[N_G(H):H] \geq p$, since $H \triangleleft
N_G(H)$. Then, by \cref{theorem29}, $\quotient{N_G(H)}{H}$ contains a subgroup
of order $p$. Such a group is of the from $\quotient{H'}{H}$ where $H'$ is a
subgroup of $N_G(H)$ containing $H$. Since $H \triangleleft N_G(H)$, we have
$H \triangleleft H'$. Finally, $|H'| = |H|\left|\quotient{H'}{H}\right| =
p^{i+1}$.
\end{proof}
\begin{definition}
A subgroup $P$ of a group $G$ is said to be a \underline{Sylow $p$-subgroup} if
$P$ is a maximal $p$-subgroup of $G$. In other words, if $P \subseteq H
\subseteq G$ with $H$ a $p$-subgroup of $G$, then $P = H$.
\end{definition}
\begin{corollary}
Let $G$ be a group of order $p^nm$ where $p$ is a prime, $n \geq 1$,
$\gcd(p,m)=1$. Let $H$ be a $p$-subgroup of $G$. Then, all the following hold:
\begin{enumerate}
\item $H$ is a Sylow $p$-subgroup if and only if $|H| = p^n$
\item Every conjugate of a Sylow $p$-subgroup is a Sylow $p$-subgroup
\item If there is only one Sylow $p$-subgroup, $P$, then $P \triangleleft G$.
\end{enumerate}
\label{corollary35}
\end{corollary}
\begin{theorem}[Second Sylow Theorem]
If $H$ is a $p$-subgroup of a finite group $G$, and $P$ is any Sylow
$p$-subgroup of $G$, then there exists $g \in G$ such that $H \subseteq
gPg^{-1}$. In particular, any two Sylow $p$-subgroups of $G$ are conjugate.
\label{sst}
\end{theorem}
\begin{proof}
Let $S$ be the set of all left cosets of $P$ in $G$, and let $H$ act on $S$ by
left multiplication. By \cref{lemma28}, we have $|S_0| \equiv |S| = [G:P]
\Mod{p}$. Since $p \nmid [G:P]$, we have $|S_0| \neq 0$. There exists $xP \in
S_0$ for some $x \in G$. Note that
\begin{align*}
xP\in S_0 &\iff hxP = xP,\quad \forall h \in H\\
&\iff x^{-1}hxP = P,\quad \forall h \in H\\
&\iff x^{-1}Hx \subseteq P\\
&\iff H \subseteq xPx^{-1}.
\end{align*}
In particular, if $H$ is a Sylow $p$-subgroup, then $|H| = |P| = |xPx^{-1}|$.
Thus, $H = xPx^{-1}$.
\end{proof}
\begin{theorem}[Third Sylow Theorem]
If $G$ is a finite group and $p$ is prime, then the number of Sylow
$p$-subgroups of $G$ divides $|G|$ and is of the form $kp+1$ for some $k \in \N
\cup \{0\}$.
\label{tst}
\end{theorem}
\begin{proof}
By the \nameref{sst}, the number of Sylow $p$-subgroups of $G$ is the number of
conjugates of any one of them, say $P$. This number is $[G:N_G(P)]$ which is a
divisor of $|G|$. Let $S$ be the set of all Sylow $p$-subgroups of $G$ and let
$P$ act on $S$ by conjugation. Then, $Q \in S_0$ if and only if $xQx^{-1} = Q$
for all $x \in P$. The latter condition holds if and only if $P \subseteq
N_G(Q)$. Both $P$ and $Q$ are Sylow $p$-subgroups of $G$ and hence of $N_G(Q)$.
Thus, by \cref{corollary35}, the are conjugate in $N_G(Q)$. Since $Q
\triangleleft N_G(Q)$, this can only occur if $Q=P$. Thus, $S_0 = \{p\}$ and by
\cref{lemma28}, $|S| \equiv |S_0| \equiv 1 \Mod{p}$. Thus, $|S| = kp+1$ for some
$k \in \N \cup \{0\}$.
\end{proof}
\begin{example}
Every group of order 15 is cyclic.
\end{example}
Let $G$ be a group of order $15 = 3 \cdot 5$. Let $n_p$ be the number of Sylow
$p$-subgroups of $G$. By the \nameref{tst}, we have $n_3 \mid 15$ and $n_3
\equiv 1 \Mod{3}$. Thus, $n_3 = 1$. Similarly, since $n_5 \mid 15$ and $n_5
\equiv 1 \Mod{5}$, $n_5 = 1$. It follows that there is only one Sylow 3-subgroup
and one Sylow 5-subgroup in $G$, say $P_3$ and $P_5$ respectively. Thus, $P_3
\triangleleft G$ and $P_5 \triangleleft G$. Consider $|P_3 \cap P_5|$, which
divides 3 and 5. Thus, $|P_3 \cap P_5| = 1$. Also, $|P_3P_5| = 15 = |G|$. It
follows that
\begin{equation*}
G \cong P_3\times P_5 \cong \quotient{\Z}{\cyclic{3}} \times
\quotient{\Z}{\cyclic{5}} \cong \quotient{\Z}{\cyclic{15}}.
\end{equation*}
\begin{example}
There are exactly two isomorphism classes of groups of order 21.
\end{example}
Let $G$ be a group of order $21 = 7 \cdot 3$. Let $n_p$ be the number of Sylow
$p$-subgroups of $G$. By the \nameref{tst}, we have $n_3 \mid 21$ and $n_3
\equiv 1 \Mod{3}$. Thus, $n_3 = 1$ or 7. Similarly, we have $n_7 \mid 21$ and
$n_7 \equiv 1 \Mod{7}$. Thus, $n_7 = 1$. It follows that $G$ has a unique Sylow
7-subgroup, say $P_7$ and note that $P_7 \triangleleft G$ and $P_7$ is cyclic,
say $P_7 = \cyclic{x}$ with $x^7 = 1$. Let $H$ be a Sylow 3-subgroup. Since $|H|
= 3$, $|H|$ is cyclic and $H = \cyclic{y}$ with $y^3 = 1$. Since $P_7
\triangleleft G$, we have $yxy^{-1} = x^i$ for some power $i \in [0,6]$. It
follows that
\begin{align*}
&\>x\\
=&\>y^3xy^{-3}\\
=&\>y^2yxy^{-1}y^{-2}\\
=&\>y^2x^iy^{-2}\\
=&\>yx^{i^2}y^{-1}\\
=&\>x^{i^3}.
\end{align*}
Since $x^{i^3} = x$ and $x^7 = 1$, we have $i^3 - 1 \equiv 0 \Mod{7}$. Then,
it must be that $i = 1,2,4$. We break this down to three cases:
\begin{enumerate}
\item If $i = 1$, then $yxy^{-1} = x$ or $yx = xy$. Thus, $G$ is abelian and
$G \cong \quotient{\Z}{\cyclic{21}}$.
\item If $i = 2$, then $yxy^{-1} = x^2$. Thus,
\begin{equation*}
G = \{ x^iy^j : 0 \leq i \leq 6,\>0 \leq j \leq 2,\> yxy^{-1} = x^2\}
\end{equation*}
which has 21 distinct elements. Here, $G$ is generated by $x$ and $y$, which are
order 3 and 7 respectively, so $G \cong \quotient{\Z}{\cyclic 3}\times
\quotient{\Z}{\cyclic 7}$.
\item If $i = 4$, then $yxy^{-1} = x^4$. Note that
\begin{equation*}
y^2xy^{-2} = yx^4y^{-1} = x^{16} = x^2.
\end{equation*}
Note that $y^2$ is also a generator of $H$. Thus, by replacing $y$ by $y^2$, we
get back to case 2.
\end{enumerate}

\pagebreak
\section{Solvable Groups}
\begin{definition}
A group $G$ is \underline{solvable} if there exists a tower of subgroups
\begin{equation*}
\{1\} = G_0 < G_1 < \dots < G_k = G
\end{equation*}
such that $G_i \triangleright G_{i+1}$ and $\quotient{G_i}{G_{i+1}}$ is abelian.
\end{definition}
\begin{remark}
$G_{i+1}$ is not necessarily a normal subgroup of $G$. However, if $G_{i+1}$ is
a normal subgroup of $G$, we get $G_i \triangleright G_{i+1}$ for free.
\end{remark}
\begin{example}
Consider the symmetric group $S_4$. Let $A_4$ be the alternating subgroup of
$S_4$ and $ V \cong \quotient{\Z}{\cyclic{2}} \times \quotient{\Z}{\cyclic{2}}$
the Klein 4 group. Note that $A_4$ and $V$ are normal subgroup of $S_4$. We have
\begin{equation*}
S_4 > A_4 > V > \{1\}.
\end{equation*}
Since $\quotient{S_4}{A_4} \cong \quotient{\Z}{\cyclic{2}}$ and
$\quotient{A_4}{V} \cong \quotient{\Z}{\cyclic{3}}$, we see that $S_4$ is
solvable.
\end{example}
\begin{theorem*}[First Isomorphism Theorem]
If $G$ and $H$ are groups and $\phi: G \to H$ is a group homomorphism, then
\begin{enumerate}
\item $\ker(\phi) \triangleleft G$
\item $\im(\phi) \leq H$
\item $\quotient{G}{\ker(\phi)} \cong \im(\phi)$.
\end{enumerate}
In particular, if $\phi$ is a surjective map, then $H \cong
\quotient{G}{\ker(\phi)}$.
\label{fit}
\end{theorem*}
\begin{theorem*}[Second Isomorphism Theorem]
If $H$ and $N$ are subgroups of a group $G$ with $N \triangleleft G$, then
$\quotient{H}{H\cap N} \cong \quotient{NH}{N}$.
\label{sit}
\end{theorem*}
\begin{theorem*}[Third Isomorphism Theorem]
If $H$ and $H$ are normal subgroups of a group $G$ such that $N \subseteq H$,
then $\quotient{H}{N}$ is a normal subgroup of $G$ and $\quotient{G}{N} \cong
\faktor{\quotient{G}{N}}{\quotient{H}{N}}$.
\label{tit}
\end{theorem*}
\begin{theorem}\leavevmode
\begin{enumerate}
\item If $G$ is a solvable group, every subgroup and every quotient group of $G$
is solvable
\item Conversely, if $N$ is a normal subgroup of a group $G$ and both $N$ and
$\quotient{G}{N}$ are solvable, then $G$ is solvable.
\end{enumerate}
In particular, a direct product of finitely many solvable groups is solvable.
\label{theorem38}
\end{theorem}
\begin{proof}\leavevmode
\begin{enumerate}
\item Suppose that $G$ is a solvable group with a tower
\begin{equation*}
\{1\} = G_0 < G_1 < \dots < G_k = G
\end{equation*}
with $G_i \triangleright G_{i+1}$ and  $\quotient{G_i}{G_{i+1}}$ is abelian.
\begin{claim}
Let $H$ be a subgroup of $G$. Then, $H$ is solvable.
\end{claim}
Define $H_i = H \cap G_i$. Since $G_{i+1} \triangleleft G_i$, we have a tower
\begin{equation*}
\{1\} = H_0 < H_1 < \dots < H_k = H
\end{equation*}
with $H_{i+1} \triangleleft H_i$. Note that both $H_i$ and $G_{i+1}$ are
subgroups of $G_i$ and $H_{i+1} = H \cap G_{i+1} = H_i \cap G_{i+1}$. Applying
the \nameref{sit} to $G_i$, we have
\begin{equation*}
\quotient{H_i}{H_{i+1}} = \quotient{H_i}{H_i \cap G_{i+1}} \cong 
\quotient{H_iG_{i+1}}{G_{i+1}} \subset \quotient{G_i}{G_{i+1}}.
\end{equation*}
Since $\quotient{G_i}{G_{i+1}}$ is abelian, so is $\quotient{H_i}{H_{i+1}}$. So
$H$ is solvable.
\begin{claim}
Let $N$ be a normal subgroup of $G$. Then $\quotient{G}{N}$ is solvable.
\end{claim}
Consider the towers
\begin{equation*}
N = G_0N < G_1N < \dots < G_kN = G
\end{equation*}
and
\begin{equation*}
\{1\} = \quotient{G_0N}{N} < \quotient{G_1N}{N} < \dots <
\quotient{G_kN}{N} = \quotient{G}{N}.
\end{equation*}
Since $G_{i+1} \triangleleft G_i$ and $N \triangleleft G$, we have
$G_{i+1}N \triangleleft G_iN$, which implies that $\quotient{G_{i+1}N}{N}
\triangleleft \quotient{G_iN}{N}$. By the \nameref{tit},
\begin{equation*}
\quotient{\quotient{G_iN}{N}}{\quotient{G_{i+1}N}{N}} \cong
\quotient{G_iN}{G_{i+1}N}.
\end{equation*}
By the \nameref{sit}, we have
\begin{equation*}
\quotient{G_iN}{G_{i+1}N} \cong \quotient{G_i}{G_i\cap G_{i+1}N}.
\end{equation*}
Since $G_{i+1} \subseteq (G_i \cap G_{i+1}N)$, there is a natural injection
$\quotient{G_i}{G_i\cap G_{i+1}N} \to \quotient{G_i}{G_i+1}$ defined by
\begin{equation*}
g + (G_i\cap G_{i+1}N) \mapsto g + G_{i+1}.
\end{equation*}
Since $\quotient{G_i}{G_{i+1}}$ is abelian, so is $\quotient{G_i}{G_i \cap
G_{i+1}N}$. Thus, $\quotient{\quotient{G_iN}{N}}{\quotient{G_{i+1}N}{N}}$ is
abelian. It follows that $\quotient{G}{N}$ is solvable.\\

Both these claims together show the first part of this theorem.
\item Suppose that $N$ is a normal subgroup of a group $G$ and both $N$ and
$\quotient{G}{N}$ are solvable.
Since $N$ is solvable, we have a tower
\begin{equation*}
\{1\} = N_0 < N_1 < \dots < N_k = N
\end{equation*}
where $N_i \triangleright N_{i+1}$ and $\quotient{N_{i+1}}{N_{i}}$ is abelian
for all $0 \leq i \leq (m-1)$. For a subgroup $H \leq G$ with $N \leq H$, which
we denote by $\bar H \coloneq \quotient{H}{N}$. Note $N \triangleleft G$ and
$N \triangleleft H$. Since $\quotient{G}{N}$, we have a tower,
\begin{equation*}
\{1\} = \quotient{N}{N} = \bar G_0 < \bar G_1 < \dots < \bar G_r = \bar G =
\quotient{G}{N}
\end{equation*}
with $\bar G_j \triangleright \bar G_{j+1}$ and $\quotient{\bar G_{j+1}}{\bar
G_j}$ for all $0 \leq j \leq (r-1)$. Let $\Sub_N(G)$ be the group of subgroups
of $G$ which contain $N$. Consider the map
\begin{align*}
\sigma : \Sub_N(G) &\to \Sub_N\left(\quotient{G}{N}\right)\\
H &\mapsto \bar H \coloneqq \quotient{H}{N}
\end{align*}
which is trivially injective. Then, by \nameref{fit}, this is a bijection. For
all $0 \leq j \leq r$, define $G_j \coloneqq \sigma^{-1}(\bar G_j)$. Since
$N \triangleleft G$, $\bar G_{j+1} \triangleleft \bar G_j$, we have
$G_{j+1} \triangleleft G_j$. Now, by \nameref{tit}, we have
\begin{equation*}
\quotient{G_j}{G_{j+1}} \cong
\quotient{\quotient{G_j}{N}}{\quotient{G_{j+1}}{N}} \cong \quotient{\bar
G_j}{\bar G_{j+1}}
\end{equation*}
which is abilian. If follows that
\begin{equation*}
\{1\} = N_0 < \dots < N_m = G_0 < \dots < G_r = G
\end{equation*}
so $G$ is solvable.
\end{enumerate}
\end{proof}
\begin{example}
$S_4$ contains subgroups isomorphic to $S_3$ and $S_2$. Since $S_4$ is solvable,
by \cref{theorem38}, $S_3$ and $S_4$ are solvable
\end{example}
\begin{definition}
A group $G$ is \underline{simple} if it is not trivial and has no normal
subgroups other than $G$ and $\{1\}$.
\end{definition}
\begin{remark}
$S_n$ is not solvable for $n \geq 5$.
\end{remark}
\begin{proof}
One can show that the alternating group $A_5$ is simple. Since $A_5 \supsetneq
\{1\}$ is the only tower and $\quotient{A_5}{\{1\}}$ is not abelian, $A_5$
is not solvable. For all $n \geq 5$, $S_5$ is a subgroup of $S_n$. Then by
\cref{theorem38}, $S_n$ is not solvable.
\end{proof}
\begin{corollary}
$G$ is a finite solvable group if and only if there exists a tower
\begin{equation*}
\{1\} = G_0 < G_1 < \dots < G_m = G
\end{equation*}
with $G_{i} \triangleright G_{i+1}$ and $\quotient{G_i}{G_{i+1}}$ is cyclic.
\label{corollary39}
\end{corollary}
\begin{proof}
Let $A$ be a finite abelian group. We have
\begin{equation*}
A \cong C_{k_1} \times \dots \times C_{k_r} 
\end{equation*}
where $C_k$ is a cyclic group of order $k$. For a finite cyclic group $C$, we
have
\begin{equation*}
C \cong \quotient{\Z}{\cyclic{p_1^{\alpha_1}}} \times \dots \times
\quotient{\Z}{\cyclic{p_r^{\alpha_r}}}
\end{equation*}
be the Chinese Remainder Theorem, with $p_i$ distinct primes. For a cyclic group
whose order is a prime power, say $\quotient{\Z}{\cyclic{p^\alpha}}$, be the
\nameref{fst}, we have a tower of subgroups
\begin{equation*}
\{1\} < \quotient{\Z}{\cyclic{p}} < \dots < \quotient{\Z}{p^{\alpha-1}} <
\quotient{\Z}{p^{\alpha-1}}
\end{equation*}
which concludes the proof.
\end{proof}

\pagebreak
\section{Automorphism Groups}
\subsection{Automorphism Groups}
\begin{definition}
Let $\quotient{E}{F}$ be a field extension. If $\psi$ is an automorphism of $E$,
in other words $\psi: E \to E$ is an isomorphism and $\psi|_F = 1_F$, we say
$\psi$ is an \underline{$F$-automorphism}. By map composition, the set
\begin{equation*}
\{\psi:E\to E\>|\>\psi\>\text{is an }F\text{-automorphism}\}
\end{equation*}
is a group. We call it the \underline{automorphism group of $\quotient{E}{F}$}
denoted by $\Aut_F(E)$.
\end{definition}
\begin{lemma}
Let $\quotient{E}{F}$ be a field extension with $f(x) \in F[x]$ and $\psi \in
\Aut_F(E)$. If $\alpha \in E$ is a root of $f(x)$, then $\psi(\alpha)$ is also a
root of $f(x)$.
\label{lemma40}
\end{lemma}
\begin{proof}
Write $f(x) = a_0 + a_1x + \dots + a_nx^n \in F[x]$. We have
\begin{align*}
f(\psi(\alpha)) &= a_0 + a_1\psi(\alpha) + a_2\psi^2(\alpha) + \dots +
a_n\psi^n(\alpha)\\
&= \psi(a_0) + \psi(a_1)\psi(\alpha) + \psi(a_2)\psi^2(\alpha) + \dots +
\psi(a_n)\psi^n(\alpha)\\ 
&= \psi(a_0 + a_1\alpha + \dots + a_n\alpha^n)\\ 
&= \psi(0)\\ &= 0.
\end{align*}
\end{proof}
\begin{lemma}
Let $E = F(\alpha_1, \dots, \alpha_n)$ be a field extension of $F$. For
$\psi_1,\psi_2 \in \Aut_F(E)$, if $\psi_1(\alpha_i) = \psi_2(\alpha_i)$ for all
$\alpha_i$, $1 \leq i \leq n$, then $\psi_1 = \psi_2$.
\label{lemma41}
\end{lemma}
\begin{proof}
Since each $\alpha \in E$ is of the form $\displaystyle \frac{f(\alpha_1, \dots,
\alpha_n)}{g(\alpha_1, \dots, \alpha_n)}$ where $f(x_1, \dots, x_n), g(x_1,
\dots, x_n)\in\\ F[x_1, \dots, x_n]$, the lemma follows.
\end{proof}
\begin{corollary}
If $\quotient{E}{F}$ is a finite extension, then $\Aut_F(E)$ is a finite group.
\label{corollary42}
\end{corollary}
\begin{proof}
Since $\quotient{E}{F}$ is a finite extension, by \cref{theorem5}, $E =
F(\alpha_1, \dots, \alpha_n)$ where $\alpha_i$ are algebraic over $F$ for all
$1 \leq i \leq n$. For $\psi \in \Aut_F(E)$, by \cref{lemma40}, $\psi(\alpha_i)$
is a root of the minimal polynomial of $\alpha_i$. Thus, there are finitely many
choices for $\psi(\alpha_i)$. By \cref{lemma41}, since $\psi \in \Aut_F(E)$ is
completely determined by $\psi(\alpha_i)$, there are finitely many choices for
$\psi$. Thus, $\Aut_F(E)$ is finite.
\end{proof}
\begin{remark}
The converse to \cref{corollary42} is false. For example, $[\R:\Q]$ in infinite,
but $\Aut_\Q(\R) = \{1\}$.
\end{remark}
\begin{definition}
Let $F$ be a field and $f(x) \in F[x]$. The \underline{Automorphism Group of
$f(x)$ over $F$} is defined to be the group $\Aut_F(E)$, where $E$ is the
splitting field of $f(x)$ over $F[x]$.
\end{definition}
From Assignment 2, we proved that the number of automorphisms is at most $[E:F]$
with equality if and only if $f(x)$ is separable over $F$, we have the following
theorem as a direct consequence.
\begin{theorem}
Let $\quotient{E}{F}$ be the splitting field of a nonzero polynomial $f(x) \in
F[x]$. We have $|\Aut_F(E)| \leq [E:F]$ with equality if and only if $f(x)$ is
separable.
\label{theorem43}
\end{theorem}
\begin{example}
Let $F$ be a field with $\ch(F) = p$ for some prime $p$ and $F^p \neq F$. Also
consider $f(x) = x^p-a$ with $a \in F \setminus F^p$. Let $\quotient{E}{F}$ be
the splitting field of $f(x)$. We have seen before that $f(x) = (x - \beta)$ for
some $\beta \in E \setminus F$. Thus, $E = F(\beta)$, Since $\beta$ can only map
to $\beta$, $\Aut_F(E)$ is trivial. Note that $|\Aut_F(E)| =1$ but $[E:F] = p$.
We have $|\Aut_F(E)| \neq [E:F]$ because $f(x)$ is not separable.
\end{example}
\begin{theorem}
If $f(x) \in F[x]$ has $n$ distinct roots in the splitting field $E$, then
$\Aut_F(E)$ is isomorphic to a subgroup of the symmetric group $S_n$. In
particular, $|\Aut_F(E)| \mid n\fact$.
\label{theorem44}
\end{theorem}
\begin{proof}
Let $X = \{\alpha_1, \dots, \alpha_n\}$ be distinct roots of $f(x)$ in $E$. By
\cref{lemma40}, if $\psi \in \Aut_E(F)$, then $\psi(X) = X$ Let $\psi|_X$ be the
restriction of $\psi$ in $X$ and $S_X$ the permutation group of $X$. The map
$\Aut_F(E) \to S_X$ defined by $\psi \mapsto \psi|_X$ is a group homomorphism.
Moreover, by \cref{lemma41}, it is injective. Thus, $\Aut_F(E)$ is isomorphic to
the subgroup of $S_n$.
\end{proof}
\begin{example}
Let $f(x) = x^3 -2 \in \Q[x]$ and $\quotient{E}{\Q}$ be the splitting field of
$f(x)$. Thus, $E = \Q(\sqrt[3]2, \xi_3)$ and $[E:\Q] = 6$. Since $\ch(\Q) = 0$,
$f(x)$ is separable. By \cref{theorem43},
\begin{equation*}
|\Aut_\Q(E)| = [E:\Q] = 6.
\end{equation*}
Also, since $f(x)$ has 3 distinct roots in $E$, by \cref{theorem44},
$\Aut_\Q(E)$ is a subgroup of $S_3$. Since the only subgroup of $S_3$ which is
of order 6 is $S_3$, we have
\begin{equation*}
\Aut_\Q(E) \cong S_3.
\end{equation*}
Furthermore, since $S_3$ is non-abelian, $\Aut_\Q(E)$ is non-abelian. This shows
Automorphism groups are need not to be abelian.
\end{example}

\subsection{Fixed Fields}
\begin{definition}
Let $\quotient{E}{F}$ be a field extension and $\psi \in \Aut_F(E)$. Define
\begin{equation*}
E^\psi \coloneqq \{ a \in E: \psi(a) = a\}
\end{equation*}
which is a subfield of $E$ containing $F$. We call $E^\psi$ the
\underline{fixed field of $\psi$}.
\end{definition}
\begin{definition}
If $G \subseteq \Aut_F(E)$, the \underline{fixed field of $G$} is defined by
\begin{equation*}
E^G \coloneqq \bigcap_{\psi \in G}E^\psi = \{ a \in E:\psi(a) = a,\>\forall \psi
\in G\}.
\end{equation*}
\end{definition}
\begin{theorem}
Let $f(x) \in F[x]$ be a separable polynomial and $\quotient{E}{F}$ its
splitting field. If $G =\Aut_F(E)$, then $E^G = F$.
\label{theorem45}
\end{theorem}
\begin{proof}
Since $F \subseteq E^G$, we have $\Aut_E^G(E) \subseteq \Aut_F(E)$. On the other
hand, if $\psi \in \Aut_F(E)$, be defintion of $E^G$, for all $a \in E^G$, we
have $\psi(a) = a$. This implies that $\psi \in \Aut_{E^G}(E)$. Thus
\begin{equation*}
\Aut_{E^G}(E) = \Aut_F(E).
\end{equation*}
Note that since $f(x)$ is separable over $F$ and splits over $E$, $f(x)$ is also
separable over $E^G$ and has $E$as its splitting field over $E^G$. Thus, by
\cref{theorem43}, we have
\begin{equation*}
|\Aut_F(E)| = [E:F] \quad\text{and}\quad |\Aut_{E^G}(E)| = [E:E^G] 
\end{equation*}
It follows that $[E:E^G] = [E:F]$. Since $[E:F]=[E:E^G]=[E^G:F]$, we have
$[E^G:F] = 1$. In other words, $E^G = F$.
\end{proof}

\pagebreak
\section{Separable and Normal Extensions}
\subsection{Separable Extensions}
\begin{definition}
Let $\quotient{E}{F}$ be an algebraic field extension. For $\alpha \in E$, let
$p(x) \in F[x]$ be the minimal polynomial of $\alpha$. We say $\alpha$ is
\underline{separable over $F$} if $p(x)$ is separable over $F$. If for all
$\alpha \in E$, $\alpha$ is separable, we say $\quotient{E}{F}$ is
\underline{separable}.
\end{definition}
\begin{theorem}
Let $\quotient{E}{F}$ be a splitting field of $f(x)\in F[x]$. If $f(x)$ is
separable, then $\quotient{E}{F}$ is separable.
\label{theorem46}
\end{theorem}
\end{document}
